Transforming Trash as an Artistic Act

### 2016-01-17 chapter3_final.tex
Relocation, turnitin fixes
Former-commit-id: e8de078896595446f38348c7c970a0b9f22fae30

% Epigraph
\begin{singlespace}
\epigraph{One day, in a rubbish heap, I found an old bicycle seat lying beside a rusted handlebar, and my mind instantly linked them together. I assembled these two objects, which everyone then recognized as a bull’s head. The metamorphosis was accomplished, and I wish another metamorphosis would occur in the reverse sense. If my bull’s head were thrown in a junk heap, perhaps one day some boy would say, \quotes{Here’s something that would make a good handlebar for my bicycle!}}{\hfill ---Pablo Picasso, \textit{Trashformations}, 1998}
\end{singlespace}

@@

% Çöpün sanatta kullanılmasının temelleri arastirilmakta.

% Ben bölümde aslında çöpün sanatta nasıl yer aldığına bakıyor olacağım. İlk kim kullanmış nasıl kullanmış. Sonrasında hangi anlamlarda kullanılmış.

Firstly I look at how artist started using objects that are not produced by herself/himself and with the purpose of making art. Early works are notable and founding ones that open new dimensions to reconsider objects and their meaning. Further, they extended the ways of art making and the language of art. Therefore, it is important and necessarry to analyze them. In other words, I first look at the foundation of using non-art objects in the art making. Early examples are analyzed and how they evolved over time is explored. I try to find out how they affected successor artist.

Secondly looked at some examples of contemporary works (or works from recent history). In particular, I try to capture the current approaches on trash. Several methods and genres are explored.  Lastly focused on the inspiring documentary of Agnes Varda, The Gleaners and I which provides a general picture of the subject.

%
%
\section{Root in the Art History}
Using trashed objects in making art can be examined with the use of non-art objects in modern art. In other words, some artist started using objects in different scope beyond their intended purpose or intended meaning and function in their modern artworks. They develop their artworks by using paper and other stuff by pasting (or juxtaposing) them together.

@@

% Resim için konu denince hep bildik tanıdık nesneler, belli bir düzenleme anlayışı (Natürmort) ya da idealize edilmiş konular, temalar akla gelir.

@@

One of the remarkable change in the 20th-century art is the use of unconventional materials in the making of paintings and sculptures, rather than the conventional materials produced with the purpose of art. These objects are not normally considered as art often because they already have a non-art function. Their place in the society and people's mind commonly have a different meaning. Beyond that, artists started to use them for their own purposes. Thus, objects gained different meanings and usages with the hands of artists. (It is explained in the previous chapter that objects are not static and absolute. Objects can be used for new purposes even if they lost their meaning and value in the conventional system.)

@@

Moreover, Braque and Picasso questioned the elitism of the art world, which had always dictated the separation of common, everyday experience from the  contemplative realm of artistic creation. Of equal importance, their work highlighted and separated the role of technical skill from art-making. Braque and Picasso introduced a “fake” element on purpose, not to mislead or fool their audience, but rather to force a discussion of art and craft, of unique and mass-produced objects. They ask: “Can this object still be art if I don’t actually render its forms myself, if the quality of the art is no longer directly tied to my technical skills or level of craftsmanship?"

% http://www.nybooks.com/articles/2010/12/09/artist-everything/
% http://www.artchive.com/artchive/S/schwitters.html
After Picasso and Baraque, many artists applied collage and assamblage techniques to their works. Dada artist Kurt Schwitters is one of the productive artists amoung them. In 1918 created his own form of Dada in Hanover called 'Merz', using rubbish materials such as labels, bus tickets and bits of broken wood in his collages and constructions. The nonsense word 'Merz' is generated from the name of the name of a bank: the Kommerz und Privatbank. Merz was soon to become a kind of brand name for almost all his activities and indeed, from 1922, he even began to refer to himself as Kurt Merz Schwitters or simply Merz.

@@

%
%
\section{The Documentary \quotes{The Gleaners and I} by Agnès Varda}
"The Gleaners and I" is a French documentary film directed by Agnès Varda in 2000. The film features various kinds of gleaning. According to the Merriam-Webster dictionary gleaning refers "to gather grain or other produce left by reapers". Varda searches for the historical and current practices of gleaning in rural and urban areas of France. Historically, gleaning is the act of collecting what is left and not profitable crops after the harvest. By combining different fragments through his film, she shows that the act of gleaning also exists in various forms and styles. In particularly she curiously focuses on the (un)familiar people who glean leftover of society. Moreover, it is a self-reflexive film because the director establishes a relationship with the practice of gleaners and her filmmaking practice. Some people glean crops; the others discarded food, and Varda gleans images.

@@

Contrary to the common act of discarding, Varda finds out a creative way to use her unconscious recorded piece that might be deleted by the others. It is the scene where Varda had forgotten to turn her camera off and accidentally films the ground and her lens cap bouncing along as she walks. She uses this scene with a jazz soundtrack at background. Watching this scene is confusing at first hand regarding context. It might be viewed as worthless and recorded by accident. One can ask that why is this placed here, what does this have to do with gleaning? However, Varda forces us to watch it (wants us to pay attention). This scene called "the dance of the lens cap". Ruth Cruickshank in the article, The Work of Art in the Age of Global Consumption: Agnes Varda’s Les Glaneurs et la glaneuse (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it. Cruickshank likened the scene to something that is normally thrown away, or in this case edited out of the film, much like the way trash is thrown away or food is left behind after a harvest. \quotes{Where many documentary makers would leave such accidental footage on the cutting room floor, Varda draws attention to how what would habitually be perceived as waste may be viewed as supplement with its own intrinsic value. Rather than literally treating it like dirt, Varda retains and prompts reassessment of that which is normally left out of shot} \cite{cruickshank2007work}. Things that are often forgotten or discarded can easily be revamped to create something useful to someone. The scene was revamped using music, and it became beautiful, much like the gleaners who found fish in the trash cooked it to make it edible, or the artist gleaner who piled discarded baby dolls into totem poles.

@@

As Varda demonstrates, people can be discovered throughout the French countryside gleaning everything from potatoes to grapes, apples to oysters, much as they did hundreds of years ago (though no longer in organized groups). Making use out of something that has been left behind and labeled as obsolete is not unique to potatoes. There is so much discarded, yet still-viable food in dumpsters that many people live off it entirely. More figuratively, there are also urban gleaners who salvage scraps from bins, appliances from the side of the road, or vegetables from stalls after the markets have been closed. By showing them she shows that once was a common practice of gleaning throughout the years has evolved, but not disappeared. She keeps light to the modern life gleaners that are not visible every time. One of them is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants. It can seen that from this example, gleaning becomes also a form of resistence to ruling system. a way of refusing to be boxed in by conventional expectations

%\todo{waste and want rules of eating from garbage.}

She shows that the act of gleaning does not bound to the collecting food and survival reasons. Some of them build their own meaning, existence and identity through the collected items. One of the examples that she gaves is that the man who collects baby dolls and use them in the decoration of his home. Every where is filled up with the babydolls even if wall of the garden.

Through the film she experiences the act of gleaning with different people. At one side she gleans potatoes in the field and on the other side follows a man with biycle look for the garbages in front of the homes. By documenting their life in action she also participates their life. But she brings her own perception to them. For example in the case of potato gleaning she collects the heart shaped ones which attract attention of her. Moreover in the case of night searching, she finds a clock without hand. It has fullfiled its function and left away. Most important part of clock is missing therefore it is not functioning. However for her it has a different meaning. Not every time people seek to be aware of time sometimes they want to forget that.

@@

Here another point is that Agnes display images of people picking up things from the ground like their ancestors. Everyone somehow collect things in their life but particularlly she selects these people and their images in action. There should be a reason for this! For some individuals, gleaning is not a novelty or a clever way to save money, but a necessity of life. They require it to sustain their life. Combine the elements from different peoples that seems totally unrelated gains powerful theme for the documentary. What gleaning means become more open (or powerful). It draws a picture of body combination of different parts (connected, dependent to the each other). The reason of gleaning varies but the fact that gleaning is continues in different forms.

@@

Varda's other subjects include artists who incorporate discarded materials into their work, symbols she discovers during her filming, and the French laws regarding gleaning versus abandoned property. Varda also spends time with Louis Pons, who explains how junk is a "cluster of possibilities." Louis Pons (born 1927) is a French collage artist. He specializes in reliefs and assemblages made entirely from discarded objects and junk. In Agnès Varda's documentary The Gleaners and I, Pons explains his artistic process and understanding of art; what others see as "a cluster of junk," he sees as "a cluster of possibilities;" and that the function of art is to tidy up one's inner and exterior worlds.

>>>>

\begin{singlespace}
\epigraph{One day, in a rubbish heap, I found an old bicycle seat lying beside a rusted handlebar, and my mind instantly linked them together. I assembled these two objects, which everyone then recognized as a bull’s head. The metamorphosis was accomplished, and I wish another metamorphosis would occur in the reverse sense. If my bull’s head were thrown in a junk heap, perhaps one day some boy would say, \quotes{Here’s something that would make a good handlebar for my bicycle!}}{\hfill ---Pablo Picasso, \textit{Trashformations}, 1998}
\end{singlespace}

@@

Firstly I look at how artist started using objects that are not produced by herself/himself and with the purpose of making art. Early works are notable and founding ones that open new dimensions to reconsider objects and their meaning. Further, they extended the ways of art making and the language of art. Therefore, it is important and necessary to analyze them. In other words, I first look at the foundation of using non-art objects in the art making. Early examples are analyzed and how they evolved over time is explored. I try to find out how they affected successor artist.

Secondly looked at some examples of contemporary works (or works from recent history). In particular, I try to capture the current approaches on trash. Several methods and genres are explored.  Lastly focused on the inspiring documentary of Agnés Varda, The Gleaners and I which provides a general picture of the subject.

\section{Root in the Art History}
Using trashed objects in making art can be examined with the use of non-art objects in modern art. In other words, some artist started using objects in different scope beyond their intended purpose or intended meaning and function in their modern artworks. They develop their artworks by using paper and other stuff by pasting (or juxtaposing) them together.

@@

@@

One of the remarkable change in the 20th-century art is the use of unconventional materials in the making of paintings and sculptures, rather than the conventional materials produced with the purpose of art. These objects are not commonly recognized as art often because they already have a non-art function. Their place in the society and people's mind commonly have a different meaning. Beyond that, artists started to use them for their own purposes. Thus, objects gained different meanings and usages with the hands of artists. It is explained in the previous chapter that objects are not static and absolute. Objects can be used for new purposes even if they lost their meaning and value in the conventional system.

@@

Moreover, Braque and Picasso questioned the elitism of the art world, which had always dictated the separation of common, everyday experience from the  contemplative realm of artistic creation. Of equal importance, their work highlighted and separated the role of technical skill from art-making. Braque and Picasso introduced a fake element on purpose, not to mislead or fool their audience, but rather to force a discussion of art and craft, of unique and mass-produced objects. They ask: “Can this object still be art if I don’t actually render its forms myself, if the quality of the art is no longer directly tied to my technical skills or level of craftsmanship?"

% http://www.nybooks.com/articles/2010/12/09/artist-everything/
% http://www.artchive.com/artchive/S/schwitters.html
After Picasso and Baraque, many artists applied collage and assemblage techniques to their works. Dada artist Kurt Schwitters is one of the productive artists among them. In 1918 created his own form of Dada in Hanover called \textit{Merz}, using rubbish materials such as labels, bus tickets and bits of broken wood in his collages and constructions. The nonsense word \textit{Merz} is generated from the name of the name of a bank: the Kommerz und Privatbank. \textit{Merz} was soon to become a kind of brand name for almost all his activities and indeed, from 1922, he even began to refer to himself as Kurt \textit{Merz} Schwitters or simply \textit{Merz}.

@@

%
%
\section{The Documentary \quotes{The Gleaners and I} by Agnès Varda}
"The Gleaners and I" is a French documentary film directed by Agnès Varda in 2000. The film features various kinds of gleaning. According to the Merriam-Webster dictionary gleaning refers "to gather grain or other produce left by reapers". Varda searches for the historical and current practices of gleaning in rural and urban areas of France. Historically, gleaning is the act of collecting what is left and not profitable crops after the harvest. By combining different fragments through his film, she shows that the act of gleaning also exists in various forms and styles. In particularly she curiously focuses on the (un)familiar people who glean leftover of society. Moreover, it is a self-reflexive film because the director establishes a relationship with the practice of gleaners and her film making practice. Some people glean crops; the others discarded food, and Varda gleans images.

@@

Contrary to the common act of discarding, Varda finds out a creative way to use her unconscious recorded piece that might be deleted by the others. It is the scene where Varda had forgotten to turn her camera off and accidentally films the ground and her lens cap bouncing along as she walks. She uses this scene with a jazz soundtrack at background. Watching this scene is confusing at first hand regarding context. It might be viewed as worthless and recorded by accident. One can ask that why is this placed here, what does this have to do with gleaning? However, Varda forces us to watch it (wants us to pay attention). This scene called "the dance of the lens cap". Ruth Cruickshank in the article, The Work of Art in the Age of Global Consumption: Agnes Varda’s \textit{Les Glaneurs et la Glaneuse} (The Gleaners and I), addressed this scene and clarified the potential deeper meaning behind it. Cruickshank likened the scene to something that is normally thrown away, or in this case edited out of the film, much like the way trash is thrown away or food is left behind after a harvest. \quotes{Where many documentary makers would leave such accidental footage on the cutting room floor, Varda draws attention to how what would habitually be perceived as waste may be viewed as supplement with its own intrinsic value. Rather than literally treating it like dirt, Varda retains and prompts reassessment of that which is normally left out of shot} \cite{cruickshank2007work}. Things that are often forgotten or discarded can easily be revamped to create something useful to someone. The scene was revamped using music, and it became beautiful, much like the gleaners who found fish in the trash cooked it to make it edible, or the artist gleaner who piled discarded baby dolls into totem poles.

@@

As Varda demonstrates, people can be discovered throughout the French countryside gleaning everything from potatoes to grapes, apples to oysters, much as they did hundreds of years ago (though no longer in organized groups). Making use out of something that has been left behind and labeled as obsolete is not unique to potatoes. There is so much discarded, yet still-viable food in dumpsters that many people live off it entirely. More figuratively, there are also urban gleaners who salvage scraps from bins, appliances from the side of the road, or vegetables from stalls after the markets have been closed. By showing them she shows that once was a common practice of gleaning throughout the years has evolved, but not disappeared. She keeps light to the modern life gleaners that are not visible every time. One of them is the teacher named Alain, an urban gleaner with a master's degree who teaches French to immigrants. It can seen that from this example, gleaning becomes also a form of resistance to ruling system ---a way of rejecting to be limited in by conventional expectations.

She shows that the act of gleaning does not bound to the collecting food and survival reasons. Some of them build their own meaning, existence and identity through the collected items. One of the examples that she gave is that the man who collects baby dolls and use them in the decoration of his home. Every where is filled up with the baby dolls even if the wall of the garden.

Through the film she experiences the act of gleaning with different people. At one side she gleans potatoes in the field and on the other side follows a man with bicycle look for the garbage in front of the homes. By documenting their life in action she also participates their life. But she brings her own perception to them. For example in the case of potato gleaning she collects the heart shaped ones which attract attention of her. Moreover in the case of night searching, she finds a clock without hand. It has fulfilled its function and left away. Most important part of clock is missing therefore it is not functioning. However for her it has a different meaning. Not every time people seek to be aware of time sometimes they want to forget that.

@@

Here another point is that Agnes display images of people picking up things from the ground like their ancestors. Everyone somehow collect things in their life but particularly she selects these people and their images in action. There should be a reason for this! For some individuals, gleaning is not a novelty or a clever way to save money, but a necessity of life. They require it to sustain their life. Combine the elements from different peoples that seems totally unrelated gains powerful theme for the documentary. What gleaning means become more open (or powerful). It draws a picture of body combination of different parts (connected, dependent to the each other). The reason of gleaning varies but the fact that gleaning is continues in different forms.

@@

Varda's other subjects include artists who include discarded objects into their work. Louis Pons is one of them. He (born 1927) is a French collage artist. He specializes in reliefs and assemblages made wholly from refused materials and trash. Pons describes his artistic process and understanding of art as what others see \quotes{a cluster of junk,} he sees \quotes{a cluster of possibilities.} By showing these people and their ideas about junk Varda presents alternative ways to see objects and invites people to rethink.

### 2016-01-17 chapter4_final.tex
Relocation, turnitin fixes
Former-commit-id: e8de078896595446f38348c7c970a0b9f22fae30

% Epigraph
\begin{singlespace}
% FROM Wild Art. quote taken from the television series `American Masters', Season 5, Episode 8, John Cage: I have nothing to say and I am saying it (aired on 17 September 1990).
\epigraph{The first question I ask myself when something doesn't seem to be beautiful is why do I think it's not beautiful? And very shortly you discover that there is no reason. If we can conquer that dislike, or begin to like what we did dislike, then the world is more open. That path ---of increasing one's enjoyment of life--- is the path, I think, we all best take: to use art not as self-expression, but as self-alteration; to become more open.}{\hfill---John Cage, \textit{Wild Art}, 2013}
\end{singlespace}

@@

%\begin{figure}
%    \begin{subfigure}[b]{0.31\textwidth}
%        \includegraphics[width=\textwidth]{project_graphics/early_works1.jpg}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.31\textwidth}
%        \includegraphics[width=\textwidth]{project_graphics/early_works2.jpg}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.31\textwidth}
%        \includegraphics[width=\textwidth]{project_graphics/early_works3.jpg}
%    \end{subfigure}
%    \caption{Examples of early works}
%    \label{fig:EarlyWorks}
%\end{figure}

@@

% NEW PART [collecting] 
\subsection{Collecting}
Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[height=6cm]{project_graphics/recycled_note.jpg}
%  \caption{Recycling notice on the package}
%  \label{fig:NoteOnPackage}
%\end{figure}

@@

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[width=1\textwidth]{project_graphics/banner1.jpg}
%  \caption{The banner carried by new grads, 2011}
%  \label{fig:Banner_1}
%\end{figure}

@@

%\begin{figure}
%    \begin{subfigure}[b]{0.48\textwidth}
%        \includegraphics[width=\textwidth]{project_graphics/tree_experiment1.jpg}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.48\textwidth}
%        \includegraphics[width=\textwidth]{project_graphics/tree_experiment2.jpg}
%    \end{subfigure}
%    \caption{Experiments with collected papers}
%    \label{fig:ExperimentWithPaper}
%\end{figure}

@@

I followed the methods of Dada poem to mix the papers used inside of the notebooks. I changed their order and direction. 
\cite{tzara1977seven}, gave the following instructions on how \quotes{[t]o make a Dadaist Poem};

\begin{quote}
Take a newspaper. Take some scissors. Choose from this paper an article the length you want to make your poem. Cut out the article. Next carefully cut out each of the words that make up this article and put them all in a bag. Shake gently. Next take out each cutting one after the other. Copy conscientiously in the order in which they left the bag. The poem will resemble you. And there you are--an infinitely original author of       charming sensibility, even though unappreciated by the vulgar herd.
\end{quote}

@@

%\begin{figure}
%    \begin{subfigure}[b]{0.31\textwidth}
%        \includegraphics[width=\textwidth]{project_graphics/exhibition1.jpg}
        %\caption{}
%        \label{fig:exhibition1}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.31\textwidth}
 %       \includegraphics[width=\textwidth]{project_graphics/exhibition2.jpg}
        %\caption{}
  %      \label{fig:exhibition2}
   % \end{subfigure}
    %\hfill
    %\begin{subfigure}[b]{0.31\textwidth}
     %   \includegraphics[width=\textwidth]{project_graphics/exhibition3.jpg}
        %\caption{}
      %  \label{fig:exhibition3}
    %\end{subfigure}
    %\caption{Installation experiments with models}
    %\label{fig:exhibition}
%\end{figure}

@@

%\begin{figure}[!tbp]
%  \centering
%  \begin{minipage}[b]{0.48\textwidth}
%    \includegraphics[width=\textwidth]{project_graphics/bilkent1.jpg}
%    \caption{Library}
%    \label{fig:BilkentLibrary}
%  \end{minipage}
%  \hfill
%  \begin{minipage}[b]{0.48\textwidth}
%    \includegraphics[width=\textwidth]{project_graphics/bilkent2.jpg}
%    \caption{Computer Laboratory}
%    \label{fig:BilkentLaboratory}
%  \end{minipage}
%\end{figure}

@@

%\begin{figure}
%    \begin{subfigure}[b]{0.48\textwidth}
%        \includegraphics[width=\textwidth]{project_graphics/torun3.jpg}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.48\textwidth}
%        \includegraphics[width=\textwidth]{project_graphics/torun2.jpg}
%    \end{subfigure}
%    \caption{Sample placement at Torun}
%    \label{fig:ExperimentWithPaper}
%\end{figure}

@@

%\begin{figure}[h!]
%  \centering
%  \includegraphics[width=1\textwidth]{project_graphics/qr_serial.jpg}
%  \caption{Sample of QR code and notebook serial}
%  \label{fig:Banner_1}
%\end{figure}

>>>>

\begin{singlespace}
% FROM Wild Art. quote taken from the television series `American Masters', Season 5, Episode 8, John Cage: I have nothing to say and I am saying it (aired on 17 September 1990).
\epigraph{The first question I ask myself when something doesn't seem to be beautiful is why do I think it's not beautiful? And very shortly you discover that there is no reason. If we can conquer that dislike, or begin to like what we did dislike, then the world is more open. That path ---of increasing one's enjoyment of life--- is the path, I think, we all best take: to use art not as self-expression, but as self-alteration; to become more open.}{\hfill---John Cage, \textit{Wild Art}, 2013}
\end{singlespace}

@@

\begin{figure}
  \begin{subfigure}[b]{0.31\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/early_works1.jpg}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.31\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/early_works2.jpg}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.31\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/early_works3.jpg}
  \end{subfigure}
  \caption{Examples of early works}
  \label{fig:EarlyWorks}
\end{figure}

@@

% NEW PART [collecting] 
\subsection{Collecting}
Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that:

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{project_graphics/recycled_note.jpg}
  \caption{Recycling notice on the package}
  \label{fig:NoteOnPackage}
\end{figure}

@@

% TODO relocate
%Trash is something that is out of sight, out of mind. Paid little attention to them and only catches attention when it is in wrong place. It is an unexpected object for people. Therefore transformation of it can create powerful and surprising effect onto the people.

%\paraphrase{Thompson comments that we only notice rubbish when it is in the wrong place, and highlights the embarrassment and anxiety that mis-placed rubbish, or rubbish which has found its way in to the wrong place can cause ‘Something which has been discarded, but never threatens to intrude, does not worry us at all.’ (1979: 92) but rubbish in the wrong place is ‘emphatically visible and extremely embarrassing’ (1972: 92). Rubbish objects are things that are no longer used or loved or cared for and often no longer seen. Rubbish objects linger on the periphery of our lives, in the back of the drawer, bottom of the wardrobe or cupboard, corner of the garage or garden shed gathering dust. (Summary From Liz Parsons.)}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{project_graphics/banner1.jpg}
  \caption{The banner carried by new grads, 2011}
  \label{fig:Banner_1}
\end{figure}

@@

\begin{figure}
  \begin{subfigure}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/tree_experiment1.jpg}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/tree_experiment2.jpg}
  \end{subfigure}
  \caption{Experiments with collected papers}
  \label{fig:ExperimentWithPaper}
\end{figure}

@@

I followed the methods of Dada poem to mix the papers used inside of the notebooks. I changed their order and direction. 
\cite{tzara1977seven}, gave the following instructions on how \quotes{[t]o make a Dadaist Poem}:

\begin{quote}
Take a newspaper. Take some scissors. Choose from this paper an article the length you want to make your poem. Cut out the article. Next carefully cut out each of the words that make up this article and put them all in a bag. Shake gently. Next take out each cutting one after the other. Copy conscientiously in the order in which they left the bag. The poem will resemble you. And there you are ---an infinitely original author of charming sensibility, even though unappreciated by the vulgar herd.
\end{quote}

@@

\begin{figure}
  \begin{subfigure}[b]{0.31\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/exhibition1.jpg}
    \label{fig:exhibition1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.31\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/exhibition2.jpg}
    \label{fig:exhibition2}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.31\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/exhibition3.jpg}
    \label{fig:exhibition3}
  \end{subfigure}
  \caption{Installation experiments with models}
  \label{fig:exhibition}
\end{figure}

@@

\begin{figure}[!tbp]
  \begin{minipage}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/bilkent1.jpg}
    \caption{Library}
    \label{fig:BilkentLibrary}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/bilkent2.jpg}
    \caption{Computer Laboratory}
    \label{fig:BilkentLaboratory}
  \end{minipage}
\end{figure}

@@

\begin{figure}
  \begin{subfigure}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/torun3.jpg}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.48\textwidth}
    \includegraphics[width=\textwidth]{project_graphics/torun2.jpg}
  \end{subfigure}
  \caption{Sample placement at Torun}
  \label{fig:SamplePlacementAtTorun}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{project_graphics/qr_serial.jpg}
  \caption{Sample of QR code and notebook serial}
  \label{fig:QR}
\end{figure}
